---
title: "Lab 1 Answer Sheet"
author: "BIOS 10602 - Multiscale Modeling of Biological Systems"
date: "9/27/2022"
output: html_document
---

## Part 3: R Markdown

3.1
```{r}
pi*(3.22E6)
```

3.2
```{r}
pi %% 1.2
```

## Part 4: Variable Assignment

4.1 a
<span style="color:blue"> A value </span>

4.1 b
<span style="color:blue"> An expression would mean it stores a reference to (3-x) instead of the value of that expression computed at creation</span>

4.2
<span style="color:blue"> Combines all arguments to form a vector all of the same type (with conversion if necessary) </span>

```{r}
myVec <- c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)
myVec
```

4.3 a
```{r}
plusFour <- myVec+4
```

4.3 b
<span style="color:blue"> Adds 4 to all the values of myVec </span>

4.4
```{r}
print(mean(myVec))
```

4.5 a
```{r}
heartRate <- seq(60,100,5)
print(heartRate)
```

4.5 b
```{r}
averageEjection <- 70
ejectionVolumes <- averageEjection * 35 * heartRate
```

4.6 a
<span style="color:blue"> Sets the first value in myVec to 3 </span>

4.6 b
<span style="color:blue"> The vector that is a subset of myVec from indices 2-5, inclusive </span>

4.6 c
<span style="color:blue"> The vector that is a subset of myVec, only the odd indices </span>

4.6 d
<span style="color:blue"> Multiplies all values in myVec by 3 </span>

4.6 e
<span style="color:blue"> Your answer here. </span>

## Part 5: Logical Expressions

5.1
<span style="color:blue"> 
taking x as the first argument, and y as the second:
1. is x not equal to y 
2. is x equal to y 
3. is x less than or equal to y
4. is x greater than or equal to y
5. is x less than y 
6. is x greater than y
</span>


5.2
<span style="color:blue"> "||" is an or operator, if either argument is true, it returns true </span>

5.3
<span style="color:blue"> 
(1) T
(2) T
(3) T
(4) F
(5) F
(6) T
(7) T
(8) F
(9) T
(10) T
(11) F
(12) F
 </span>

5.4
<span style="color:blue"> Indexes vector multiplesOfFive for all that are not divisible by 10 </span>

5.5 a
<span style="color:blue"> It treats TRUE as 1 and FALSE as 0 </span>

5.5 b
<span style="color:blue"> It makes it easy to check for non zero values </span>

## Part 6: Control Flow: if, else

6.1
<span style="color:blue"> 0 is a "falsy" value, so the first block isn't executed, the second one is </span>

6.2 a
<span style="color:blue"> It checks if carSpeed is greater than speedLimit and prints the "Give ticket" if greater than, and "Do nothing" if equal to</span>

6.2 b
<span style="color:blue"> The block with the print statement "Give ticket" is executed </span>

6.3
```{r}
bodyTemp <- 37.0
if ((bodyTemp > 37.2) || (bodyTemp < 36.5)) {
    print("seek medical attention")
} else {
    print("do nothing")
}
```

6.4
```{r}
if ((bodyTemp > 37.2) || (bodyTemp < 36.5)) {
    print("seek medical attention")
    if (bodyTemp > 37.2) {
        print("fever")
    } else {
        print("hypothermia")
    }
} else {
    print("do nothing")
}

```

## Part 7: Control Flow - Loops

7.1 a
<span style="color:blue"> For every value from 1 through 10 (inclusive) print that value multiplied by 2</span>

7.1 b
<span style="color:blue"> In the first line of the if statement and changes each iteration </span>

7.1 c
<span style="color:blue"> it is </span>

7.1 d
<span style="color:blue"> It does not, i is overwritten </span>

7.2 a
<span style="color:blue"> If the remainder when divided by 2 is 0 </span>

7.2 b
```{r}
for (i in 1:12) {
    if (i %% 2 == 0) {
        print(i)
    }
    if (i == 7) {
        print(i)
    }
}
```

7.3
```{r}
for (letter in letters) {
    print(toupper(letter))
}
```

7.4 a
<span style="color:blue"> The value of x only decreases, and starts below 0 </span>

7.4 b
<span style="color:blue"> Starting at positive 10 </span>

7.5 a
<span style="color:blue"> It would print 4 over and over because the value of x is never changed </span>

7.5 b
```{r}



x <- 2  
while(x <=  5){  
    print(x)
	x <- x+x
}  
```

## Part 8: Functions in R

8.1 a
```{r}
findCube <- function(n) {
    return(n**3)
}
```

8.1 b
```{r}
cubed <- findCube(529)
```

8.2
<span style="color:blue"> They are assigned in the order they are put in the function </span>

8.3 a
```{r}
calcMean <- function(vec) {
    return(sum(vec)/length(vec))
}
```

8.3 b
```{r}
testVec <- seq(3,14,1)
```

8.3 c
```{r}
print(calcMean(testVec) == mean(testVec))
```

8.4 a
```{r}
hpluses <- numeric(14)
for (pH in seq(1,14,1)) {
    hpluses[pH] = 1*10^(-pH)
}
```

8.4 b
```{r}
H_from_pH <- function(pH) {
    return(1*10^(-pH))
}
OH_from_pH <- function(pH) {
    return(1*10^(-(14-pH)))
}
```